\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-11-06 jss/article.tex
small mod

In the other two cases, Poisson and Binomial, the prior distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Uniform($0, \infty$) for the Gaussian. As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if $k\ge2$ and a covariate matrix has a full rank. The Poisson model, however, can have such posterior propriety if $k\ge2$ and the second-level mean is known. The efficiency of these priors is explored in the examples in section 5.

>>>>

In the other two cases, Poisson and Binomial, the improper prior uniform distribution of $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($B_{j}$) as does $A$ with Uniform($0, \infty$) for the Gaussian. As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if $k\ge2$ and a covariate matrix has a full rank. The Poisson model, however, can have such posterior propriety if $k\ge2$ and the second-level mean is known. The efficiency of these priors is explored in the examples in section 5.
